---
title: "useR!2019 - Tutorials: Packages development"
output: html_notebook
---

Source: https://github.com/jennybc/pkg-dev-tutorial

##Partie 1 : Introduction

```{r,eval=F}
.Library
.libPaths()
installed.packages()
```

```{r}
library(tidyverse)
```

```{r}
ipt <- installed.packages() %>% as_tibble()
ipt
```

```{r}
nrow(ipt)


```

```{r}
ipt %>% dplyr::count(LibPath,Priority)
```

```{r}
devtools::install_github("jimhester/lookup")
```

Create a package :

```{r}
usethis::create_package("foofactors")
```

Open a new Rsession window, directory with new project environment file.

Adapted from the Whole Game : r-pkgs.orgs/whole-game.html

Factors can be vexing : creation of a first function fbind

define function inside rsession project :
```{r,eval=F}
usethis::use_r("fbind")
```


```{r}
source("foofactors/R/fbind.R")
(a <- factor(c("character","hits","your","eyeball")))
(b <- factor(c("but","where it","integer")))
fbind(a,b)
```

Best way to source :

```{r}
devtools::load_all()
```

fbind don't exist in global environment != de source

Editer son Rprofile :
```{r}
usethis::edit_r_profile()
```
Ne pas load de packages dedans !

```{r}
usethis::use_partial_warnings()
```


```{r}
devtools::check()
```


```{r}
use_mit_license("Vincent ROCHER")
```

scaffold documentation :
```{r}
devtools::document()
```

use_github() créer un nouveau depot sur github

##Partie 2 : testing


```{r}
insert_into <- function(x,y,where = 1){
  if(where == 1) {
    cbind(y,x)
  }else if (where > ncol(x)){
    cbind(x,y)
  }else {
    lhs <- (1:where)
    cbind(x[lhs],y,x[-lhs])
  }
}


df1 <- data.frame(a = 3,b = 4,c = 5)
df2 <- data.frame(X = 1, Y = 2)
insert_into(df1,df2,where = 1)
insert_into(df1,df2,where = 2)
insert_into(df1,df2,where = 3)
```

Create a function file with devtools::use_r("insert_into")

```{r}
usethis::use_test()
```

Créer un script R dans test
Ensuite on lance devtools::test() qui lance testthat::test_file() pour tous les fichiers tests du directory

devtools::test_coverage_file() regarde si toutes les lignes des fonctions ont été testées. Si non, ajouter un test dans ce cas là

##Partie 3: Document and share 

Turn a packages into a website -> pkgdown 
